### 2016-05-12 README.Rmd
update README to with updated username for travis

>>>>

<!-- add a TravisCI badge -->
<!-- Add an appVeyor badge -->
[![Travis-CI Build Status](https://travis-ci.org/njtierney/visdat.svg?branch=master)](https://travis-ci.org/njtierney/visdat) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/visdat)
